---
title: "Kermit Perceptions Rank Based Test"
author: "Lydia Bleifuss"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Lydia's first message, excellllent. 


This is Claire the collab master
- load tidyverse
- read in the kermit data as 'kermit'
- make some side-by-side histograms of the Score.pre for all respondents, seperated by the Gender column


```{r}
library(tidyverse)


kermit <- read_csv("Kermit.csv")


kermit_hist <- ggplot(kermit, aes(x = Score.pre))+
  geom_histogram(bins = 4)+
  facet_wrap(~Gender)

kermit_hist
```


Creator: Perform rank based comparisons using Mann-Whitney U and Wilcoxon-Signed Rank

Question: Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents? 

```{r}
#compares ranks with unpaired data
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

# Null hypothesis: There is NOT a significant difference in ranks for male and female respondents
# Alternative: There IS a significant difference in ranks

mwu_kermit

```

There was no significant difference in ranks for male and female respondents (W = 1.55, p = 0.4, alpha = 0.05 (use in line referencing))
